---
Week 14 IP Part 4: Anomaly Detection
author: "Lawrence Ondieki"
date: "20/7/2021"
output:
  html_document:
    df_print: paged
---

# Problem Definition

## **a) Specifying the Question**

Identify anomalies in the dataset = fraud detection

## **b) Defining the metrics for success**

To check whether there are any anomalies in the given sales dataset. The
objective of this task being fraud detection.

## **c) Understanding the context**

You are a Data analyst at Carrefour Kenya and are currently undertaking
a project that will inform the marketing department on the most relevant
marketing strategies that will result in the highest no. of sales (total
price including tax). Your project has been divided into four parts
where you’ll explore a recent marketing dataset by performing various
unsupervised learning techniques and later providing recommendations
based on your insights.

## **d) Relevance of the data**

The data used for this project will inform the marketing department on
the most relevant marketing strategies that will result in the highest
no. of sales (total price including tax)

\[<http://bit.ly/CarreFourSalesDataset>\].

# Data Analysis


```{r}
# loading libraries
library(data.table)
library(tidyverse)
```

```{r}
library(anomalize)
```

```{r}
# importing our data
# reading our data
df <- fread('http://bit.ly/CarreFourSalesDataset')
df
```
## Anomaly detection

```{r}
library(data.table)
library(psych)
```

```{r}
library(mvtnorm)
library(caret)
```

```{r}
library(PRROC)
summary(df)
```

```{r}
skew <- sum(as.numeric(df$Class))/nrow(df)
sprintf('Percentage of fraudulent transactions in the data set %f', skew*100)
```
# There were no frauduent transactions in the data

