---
Week 14 IP Part 3: Association Rules
author: "Lawrence Ondieki"
date: "20/7/2021"
output:
  html_document:
    df_print: paged
---

# Problem Definition

## **a) Specifying the Question**

Create association rules that will allow you to identify relationships between variables in the dataset.

## **b) Defining the metrics for success**

Create association rules that will help identify relationships between variables in the dataset.
Provide insights for our analysis.

## **c) Understanding the context**

You are a Data analyst at Carrefour Kenya and are currently undertaking
a project that will inform the marketing department on the most relevant
marketing strategies that will result in the highest no. of sales (total
price including tax). Your project has been divided into four parts
where you’ll explore a recent marketing dataset by performing various
unsupervised learning techniques and later providing recommendations
based on your insights.


## **e) Relevance of the data**

The data used for this project will inform the marketing department on
the most relevant marketing strategies that will result in the highest
no. of sales (total price including tax)

\[<http://bit.ly/SupermarketDatasetII>\].

# Data Analysis



```{r}
# loading libraries
library(relaimpo)

library(data.table)
library(ggplot2) # Data visualization
library(ggthemes) # Plot themes
library(plotly) # Interactive data visualizations
library(dplyr) # Data manipulation
library(psych) # Will be used for correlation visualization
library(arules)# for association
# importing our data
# reading our data
path <-"http://bit.ly/SupermarketDatasetII"
df<-read.transactions(path, sep = ",")
```



```{r}
df
```

## Data Checking

```{r}
# previewing the column names
colnames(df)
```

    
```{r}
# verifying the class of the data
class(df)
```
```{r}
# Previewing our first 5 transactions
inspect(df[1:5])
```

```{r}
# Alternatively,
# preview the items that make up our dataset
items<-as.data.frame(itemLabels(df))
colnames(items) <- "Item"
head(items, 10)    
```

```{r}
# Generating a summary of the dataset
summary(df)
```

    

```{r}
# Exploring the frequency of some articles 
itemFrequency(df[, 8:10],type = "absolute")
```

   
```{r}
round(itemFrequency(df[, 8:10],type = "relative")*100,2)
```
```{r}
# Producing a chart of frequencies and fitering 
# Displaying top 10 most common items in the transactions dataset 
# and the items whose relative importance is at least 10%
par(mfrow = c(1, 2))

# plot the frequency of items
itemFrequencyPlot(df, topN = 10,col="darkgreen")
itemFrequencyPlot(df, support = 0.1,col="darkred")
```


```{r}
# Building a model based on association rules using the apriori function 
# We use Min Support as 0.001 and confidence as 0.8
rules <- apriori (df, parameter = list(supp = 0.001, conf = 0.8))
```

```{r}
rules
```

```{r}
# using the  measures of significance and interest on the rules,determining which ones are interesting and which to discard.
# Building a apriori model with Min Support as 0.002 and confidence as 0.8.
rules2 <- apriori (df,parameter = list(supp = 0.002, conf = 0.8)) 
```

```{r}
# Building apriori model with Min Support as 0.002 and confidence as 0.6.
rules3 <- apriori (df, parameter = list(supp = 0.001, conf = 0.6)) 
```


```{r}
rules2
```


```{r}
rules3
```

The first model had 74 rules while the second has 2. these had a confidence level of 0.8 but different minimum supports. the same applies to the third that had 545 rules. from this , we can conclude that a higher support level equals a loss in the rules while a low confidence level equals a g=higher number of rules, though not all of them will be useful.


```{r}
# performing an exploration of our model through the use of the summary function as shown
summary(rules)
```


The summary gives us the statistical data about the rules. this is inclusive of the support, confidence and also lift


```{r}
# Observing rules built in our model i.e. first 5 model rules
inspect(rules[1:5])
```

Interpretation of the rules:
1. If someone buys frozen smoothie and spinach, they are 89% likely to buy mineral water too
2. If someone buys bacon and pancakes, they are 81% likely to buy spaghetti too
3. If someone buys nonfat milk and turkey, they are 82% likely to buy mineral water too
4. If someone buys ground beef and nonfat milk, they are 86% likely to buy mineral water too
5. If someone buys frozen mushroom cream sauce and pasta, they are 95% likely to buy escalope too


```{r}
# Ordering these rules by a criteria such as the level of confidence
# then looking at the first five rules.
rules<-sort(rules, by="confidence", decreasing=TRUE)
inspect(rules[1:5])
```

# Interpretation
# Four of the given five rules have a confidence of 100 and the fifth rule has a confidence of 95


```{r}
# If we're interested in making a promotion relating to the sale of milk, 
# we could create a subset of rules concerning these products 
# ---
# This would tell us the items that the customers bought before purchasing milk
# ---
# 
milk <- subset(rules, subset = rhs %pin% "milk")
 
# Then order by confidence
milk<-sort(milk, by="confidence", decreasing=TRUE)
milk
```

```{r}
inspect(milk[1:5])
```

```{r}
# What if we wanted to determine items that customers might buy 
# who have previously bought milk?
# ---
# 
# Subset the rules
milk <- subset(rules, subset = lhs %pin% "milk")

# Order by confidence
milk<-sort(milk, by="confidence", decreasing=TRUE)

# inspect top 5
inspect(milk[15:19])
```
